Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-18 content/contribution/CoDeR.tex
moved first draft of CoDeR description to backup file, started again in used file

\begin{nestedsection}{CoDeR Model for Continuous Deductive Reasoning}{model}
	Stream-based Data Model

	Minimal Algebra

>>>>

\begin{nestedsection}{CoDeR Model for Continuous Deductive Reasoning}{model}
	CoDeR is an abstract model for continuous deductive reasoning over streamed RDF data that expresses the semantics of Continuous Datalog.
	It is composed of a stream-based data model for expressing the streams $S$, $P$ and $N$ of each ${CDP = \{A,S,R\} \vDash \{A',P,N\}}$, and a minimal algebra of stream-to-stream operators for expressing the persistent set of axiomatic rules $A$.
	It casts the problem of applying those rules to streamed RDF data as that of iterative pattern matching, in a manner inspired by the Rete pattern matching algorithm \citep{forgy79}, though it is meant to support any such algorithm rather than prescribing one itself.

	% Stream-based Data Model

	% Minimal Algebra
